---
title: "Regression Models - Quiz 02"
author: "Utkarsh Ashok Pathrabe"
output: md_document
---

Quiz 02
=======  

|Attempts|Score|  
|:------:|:---:|  
|   1/3  |10/10|  

Question 01
-----------  
Consider the following data with x as the predictor and y as as the outcome.  
```{r warning=FALSE, error=FALSE}
x <- c(0.61, 0.93, 0.83, 0.35, 0.54, 0.16, 0.91, 0.62, 0.62)
y <- c(0.67, 0.84, 0.6, 0.18, 0.85, 0.47, 1.1, 0.65, 0.36)
```  
Give a P-value for the two sided hypothesis test of whether $\beta_1$ from a linear regression model is 0 or not.  

### Answer  
0.05296  

#### Explanation  
```{r warning=FALSE, error=FALSE}
f <- lm(y ~ x)
summary(f)
```  

Question 02
-----------  
Consider the previous problem, give the estimate of the residual standard deviation.  

### Answer  
0.223  

#### Explanation  
```{r warning=FALSE, error=FALSE}
summary(f)
```  

Question 03  
-----------  
In the `mtcars` data set, fit a linear regression model of weight (predictor) on mpg (outcome). Get a 95% confidence interval for the expected mpg at the average weight. What is the lower endpoint?  

### Answer  
18.991  

#### Explanation  
```{r warning=FALSE, error=FALSE}
data(mtcars)
x <- mtcars$wt
y <- mtcars$mpg
fit <- lm(y ~ x)
predict(fit, data.frame(x = mean(x)), interval = "confidence")
```

Question 04
-----------  
Refer to the previous question. Read the help file for `mtcars`. What is the weight coefficient interpreted as?  

### Answer  
The estimated expected change in mpg per 1,000 lb increase in weight.  

#### Explanation  
```{r warning=FALSE, error=FALSE, eval=FALSE}
help(mtcars)
```

Question 05
-----------  
Consider again the `mtcars` data set and a linear regression model with mpg as predicted by weight (1,000 lbs). A new car is coming weighing 3000 pounds. Construct a 95% prediction interval for its mpg. What is the upper endpoint?  

### Answer  
27.57  

#### Explanation  
```{r warning=FALSE, error=FALSE}
predict(fit, data.frame(x = mean(3)), interval = "prediction")
```  

Question 06
-----------  
Consider again the `mtcars` data set and a linear regression model with mpg as predicted by weight (in 1,000 lbs). A "short" ton is defined as 2,000 lbs. Construct a 95% confidence interval for the expected change in mpg per 1 short ton increase in weight. Give the lower endpoint.

### Answer  
-12.973  

#### Explanation  
```{r warning=FALSE, error=FALSE}
fit2 <- lm(y ~ I(x / 2))
tbl2 <- summary(fit2)$coefficients
mean <- tbl2[2,1]      
se <- tbl2[2,2] 
df <- fit2$df
#Two sides T-Test
mean + c(-1,1) * qt(0.975, df = df) * se
```  

Question 07
-----------  
If my X from a linear regression is measured in centimeters and I convert it to meters what would happen to the slope coefficient?  

### Answer  
It would get multiplied by 100.  

#### Explanation  
```{r warning=FALSE, error=FALSE}
summary(fit)$coefficients[2, 1]
fit3 <- lm(y ~ I(x / 100))
summary(fit3)$coefficients[2, 1]
```  

Question 08
-----------  
I have an outcome, $Y$, and a predictor, $X$ and fit a linear regression model with $Y = \beta_0 + \beta_1 X  + \epsilon$ to obtain $\hat \beta_0$ and $\hat \beta_1$. What would be the consequence to the subsequent slope and intercept if I were to refit the model with a new regressor, $X + c$ for some constant, $c$?  

### Answer  
The new intercept would be $\hat \beta_0 - c \hat \beta_1$.  

Question 09
-----------  
Refer back to the mtcars data set with mpg as an outcome and weight (wt) as the predictor. About what is the ratio of the
the sum of the squared errors, \(\sum_{i=1}^n (Y_i - \hat Y_i)^2\) when comparing a model with just an intercept (denominator) to
the model with the intercept and slope (numerator)?  

### Answer  
0.25  

#### Explanation  
```{r warning=FALSE, error=FALSE}
fitRes <- fit$residuals ^ 2
fitIntercept <- lm(mpg ~ 1, mtcars)
fitInterceptRes <- fitIntercept$residuals ^ 2
sum(fitRes) /sum(fitInterceptRes)
```  

Question 10
-----------  
Do the residuals always have to sum to 0 in linear regression?  

### Answer  
If an intercept is included, then they will sum to 0.  